Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-03-31 cbm-rbd-paper.tex
revision documents

The third scenario consists of component failure times taht are later than expected,
obtained by simulating Weibull lifetimes using $\lambda_k = 2 \ykz$ for all four component types.
The results are depicted in Figure~\ref{fig:br1sim3fig5Tt01}.

>>>>

The third scenario consists of component failure times that are later than expected,
obtained by simulating Weibull lifetimes using $\lambda_k = 2 \ykz$ for all four component types.
The results are depicted in Figure~\ref{fig:br1sim3fig5Tt01}.
